Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-07-19 R0V0.tex
> Done: Finished to review. Need to send to Ian.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{xcolor}
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{./imgs}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, input-affine nonlinear systems are considered. The problem under consideration is to design structured (for instance, decentralized or distributed) controllers for this class of systems. Although control-Lyapunov functions are the natural candidate to design these feedback laws, in terms of dynamical programming, the search for these functions is non-convex \cite{Rantzer:2001}. On the other hand, control-contraction metrics provide controllers that render pairs of solutions exponentially converge to each other. Moreover, the search for a structured controller and a suitable metric can be formulated in terms of a convex optimization problem. Under block-diagonal dominance conditions, this convex optimization problem can also be distributed. An example illustrate the approach for a network system.
\end{abstract}

@@

Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure. The main concept employed for the control of dynamic systems is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}. In terms of computation, controller design problems are often translated in terms of dynamic programming.

For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}. The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}.

In the case of nonlinear systems, systematic approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}. These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}. In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.

@@

An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation of the system is considered. The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below). This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

@@

Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}. For such systems, a property often sought is the ability to augment or to reduce the size of the network without computing the controller for all subsystems, i.e., to make the controller scalable. In some cases, this property is satisfied by desnigning controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).

@@

For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs, in this work. The systems under consideration are continuously differentiable and affine in the input. One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed similarly to Lyapunov functions to measure the exponential convergence of pairs of solutions. Employing CCMs, the design of a structured feedback law allowing exponential convergence of solution is obtained in two steps.

The first step consists of an off-line computation. The original system is extended with its \emph{differential / variational} formulation. The exponential convergence is reformulated in terms of stability of the origin for the extended system. This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint. The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law.

The second step consists of an on-line integration. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).

\todo[inline]{Highlight the difference between this paper and \cite{Manchester2014a} by saying that this one the integration part is also distributed.}

At this point, the three contributions of this work can be highlighted. First, a systematic framework for off-line computation of a structured controller and metric for nonlinear systems is provided. This framework is the formulation of a convex optimization problem whose computation can also be distributed, provided that some conditions are met. Second, the computation of the online integration phase can distributed, due to the structure imposed on the metric. Third, the structure impose on the controller allows to address the scalability issue of CCMs. Note that the proposed method provides an explicit formula for the controller, since it is constructive.

Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature. These are mostly related to network systems. For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis. This paper contrast with these works mainly in two points: 1) A systematic framework  for structured controller design is proposed; 2) Due the formulation of the stabilization as a convex optimization problem, not only a explicit formula of a structured controller is obtained but also a metric.

\paragraph{Overview.} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}. The background needed for this paper is stated in Section \ref{sec:background}. Section \ref{sec:Results} presents the result of this paper. Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}. The proofs of the results are provided in Section \ref{sec:Proof of the Results}. Section \ref{sec:Conclusion} collects final remarks.

\paragraph{Notation.} Let $N\in\mathbb{N}$ be a constant value. The notation $\mathbb{N}_{[1,N]}$ stands for the set $\{i\in\mathbb{N}:1\leq i\leq N\}$. Let $c\in\mathbb{R}$ be a constant value. The notation $\mathbb{R}_{[1,c]}$ (resp. $\mathbb{R}_{\diamond c}$) stands for the set $\{x\in\mathbb{R}:1\leq x\leq c\}$ (resp.  $\{x\in\mathbb{R}:x\diamond c\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi) definite.

The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}\to\mathbb{R}^m$ that are locally essentially bounded. Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$.

@@

\noindent{\itshape Class of systems.} Consider the class of systems described by the differential equation
\begin{equation}\label{eq:general system}
	\dot{x}(t)=f(x(t))+B(x(t))u(t),	
\end{equation}
where, for positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively. The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and satisfy $f(0)=0$ and $B(0)=0$. From now on the dependence of on the time $t$ will be omitted.

@@

{\itshape Stabilizability Notion.} A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$, denoted as $k^\ast(\cdot,\cdot,X^\ast,u^\ast)$, such that the inequality
\begin{equation}\label{eq:global exponential uniform stabilizability}
	\left|X(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
\end{equation}
holds true, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}). Note that this not is a particular case of \emph{incremental asymptotic stability}, the interested reader may address \cite{Forni2014,Forni2014a} for further information on this stability concept.

Note that a stronger condition than the global exponential stabilizability of a particular solution is the requirement that every forward complete solution of the system is globally exponentially stabilizable. This concept is formalized in the following definition recalled from \cite{Manchester2014a}.

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:global exponential uniform stabilizability}.
\end{definition}

@@

For each component $i\in\mathbb{N}_{[1,m]}$ of the feedback law $k^\ast=(k_1^\ast,\ldots,k_m^\ast)^\top$, denote the set of indexes
\begin{equation*}
	\mathscr{K}(i)=\left\{j\in\mathbb{N}_{[1,n]}:k_i^\ast\ \text{depends explicitely on}\ x_j \right\}.
\end{equation*}
The definition of the set $\mathscr{K}(\cdot)$ encompasses different structures. For instance, when $m=n$ full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$. This is formalized by letting $\mathscr{K}(i)=\{i\}$. Moreover, at points where $k_i^\ast$ is differentiable, the explicit dependence on $x_i$ means that, for every index $j\in\mathbb{N}_{[1,n]}$ with $j\neq i$, $\partial k_i^\ast/\partial x_j\equiv0$.

@@

\begin{problem}\label{problem formulation}\hfill
	\begin{enumerate}
		\item Find a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$ for system \eqref{eq:general system} that globally exponentially uniformly stabilizes any forward complete solution $X(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system};

		\item The function $k^\ast=(k_1^\ast,\ldots,k_m^\ast)$ belongs to the set $\Xi$.
		\end{enumerate}
\end{problem}

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology) for network systems rendering it universally stabilizable. Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.
\end{equation}
Section \ref{sec:Illustration} shows how the approach proposed in this work is employed to design a decentralized controller for the network composed by interconnections of system \eqref{eq:example}.

@@

A suitable framework to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by 
\begin{equation*}
	A_{jk}(x,u)=\dfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)	
\end{equation*}
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{align}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x\leq\ -2\lambda \delta_x^\top M\delta_x\label{eq:}
		\end{align}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition for contraction. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

@@

\begin{theorem}\label{prop:CCM Existence}
	If there exists a control-contraction metric for system \eqref{eq:general system}, then there exists a solution to item 1 of Problem~\ref{problem formulation}.
\end{theorem}

Another important result of Theorem \ref{prop:CCM Existence} the feedback for system \eqref{eq:general system} obtained by integrating a feedback law designed for system \eqref{eq:general system:differential}.

As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with respect to a control-Lyapunov function is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.

@@

{\itshape Motivation.} From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.

{\itshape Contribution.} In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$. Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:contracting feedback law}.

@@

Definition~\ref{def:SSCCM} implies that there exist integers $N>1$ and $n_i>0$ such that $n_1+\ldots+n_N=n$. Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i),
	\end{equation*}
for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$.

In other words, a sum-separable metric is the case in which the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these components depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$. The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).

@@

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

\begin{corollary}\label{cor:distributed computation}
	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
	\begin{equation}\label{eq:MI formulation:i}
		T_{ii}\preceq 0
	\end{equation}
	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation}.
\end{corollary}

@@

\todo[inline]{See the works of Ahmadi (Princeton) on scale-diag. dom.}

@@

Although the requirement of a sum-separable structure seems to be restrictive, for some classes of systems this structure is equivalent to the (possibly local) stability of the origin.

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{xcolor}
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{./imgs/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, input-affine nonlinear systems are considered. The problem under consideration is the design of structured (for instance, decentralized or distributed) controllers for this class of systems. Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, the search for these functions is non-convex \cite{Rantzer:2001}. On the other hand, control-contraction metrics can provide controllers through a convex optimization problem. The drawback is that it may require the a function with $n^2$ elements. By exploiting sparsity, this number of verification can be decreased and the convex optimization problem can also be distributed. An example illustrates the approach for a network system.
\end{abstract}

@@

Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure. The main underlying concept employed for the synthesis of feedback laws is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}. In terms of computation, controller design problems are often translated in terms of dynamic programming.

For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}. The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}. In the case of nonlinear systems, design approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}. These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}. In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.

@@

An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered. The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed trajectory (see a precise definition below). This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

@@

Large-scale systems may appear in the form of interconnection of smaller components, for example, in applications such as traffic networks \cite{CanudasdeWitMorbidiLeonOjedaEtAl2015}, pipe networks \cite{Persis2011a} and sensor networks \cite{Pajic2011}. For such systems, a property often desired is the ability to synthetize controllers with particular structures (see \cite{Siljak1991,Bai2011} for distributed controllers).

@@

For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints, in this work. The systems under consideration are continuously differentiable and affine in the input. One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions. Employing CCMs that can be decomposed into the sum of smaller elements, the design of a structured feedback law allowing exponential convergence of solutions is obtained in two steps.

The first step consists of an off-line computation. The original system is extended with its \emph{differential / variational} formulation. The exponential convergence problem is reformulated in terms of stability of the origin for the extended system. This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint. The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law. The second step consists of an on-line optimization. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).

At this point, the three contributions of this work can be highlighted. First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structure constraint, a feedback law with prescribed structure is obtained for nonlinear systems. Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is distributed. Third, when the system is described a non-strongly connected graph, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability. Note that the proposed method provides an explicit formula for the controller, since it is constructive.

Other works related to analysis under structural constraints to achieve exponential convergence of solutions do exist in the literature. For contraction analysis, see \cite{Aminzare2014a} for analysis according to different network topologies and \cite{Andrieu2016} for transversal contraction analysis. This paper contrast with these works mainly in two points: 1) A  methodology for the design of structured controllers is proposed; 2) Due the formulation of the stabilization problem as a convex optimization problem, an explicit formula of a structured controller is obtained.

\paragraph{Overview.} The motivation and the problem formulation are provided in Section \ref{sec:Problem Formulation and Motivation}. The background needed for this paper is stated in Section \ref{sec:background}. Section \ref{sec:Results} presents the main result of this paper. Illustrations of the proposed approach are provided in Section \ref{sec:Illustration}. The proofs of the results are provided in Section \ref{sec:Proof of the Results}. Section \ref{sec:Conclusion} collects final remarks.

\paragraph{Notation.} Let $N\in\mathbb{N}$ be a constant value. The notation $\mathbb{N}_{[1,N]}$ stands for the set $\{i\in\mathbb{N}:1\leq i\leq N\}$. Let $c\in\mathbb{R}$ be a constant value. The notation $\mathbb{R}_{[1,c]}$ (resp. $\mathbb{R}_{\diamond c}$) stands for the set $\{x\in\mathbb{R}:1\leq x\leq c\}$ (resp.  $\{x\in\mathbb{R}:x\diamond c\}$, where $\diamond$ is a comparison operator, i.e., $\diamond\in\{<,\geq,=,\ \text{etc}\}$). A matrix $M\in\mathbb{R}^{n\times n}$ with zero elements except (possibly) those  $m_{ii},\ldots,m_{nn}$ on the diagonal is denoted as $\mathbin{\mathtt{diag}}(m_{ii},\ldots,m_{nn})$. The notation $M\succ 0$ (resp. $M\succeq 0$) stands for $M$ being positive (resp. semi)definite.

The notation $\mathcal{L}_{\mathrm{loc}}^\infty(\mathbb{R}_{\geq0},\mathbb{R}^m)$ stands for the class of functions $u:\mathbb{R}\to\mathbb{R}^m$ that are locally essentially bounded. Given differentiable functions $M:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $f:\mathbb{R}^n\to\mathbb{R}^n$ the notation $\partial_fM$ stands for matrix with dimension $n\times n$ and with $(i,j)$ element given by $\frac{\partial m_{ij}}{\partial x}(x)f(x)$. The notation $f'$ stands for the total derivative of $f$.

@@

\noindent{\itshape Class of systems.} Consider the class of systems described by the differential equation
\begin{equation}\label{eq:general system}
	\dot{x}(t)=f(x(t))+B(x(t))u(t),	
\end{equation}
where, for positive times $t$, the \emph{system state} $x(t)$ and the \emph{system input variable} $u(t)$ evolve in the Euclidean spaces $\mathbb{R}^n$ and $\mathbb{R}^m$, respectively. The functions $f:\mathbb{R}^n\to\mathbb{R}^n$ and $B:\mathbb{R}^n\to\mathbb{R}^m$ are assumed to be smooth, i.e., infinitely differentiable and to satisfy $f(0)=0$ and $B(0)=0$. From now on the dependence on the time $t$ will be omitted.

@@

{\itshape Stabilizability Notion.} A forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system} is said to be  \emph{globally exponentially uniformly stabilizable} with \emph{rate} $\lambda>0$ if there exist a constant value $C>0$ and a feedback law $k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m$, denoted as $k^\ast(\cdot,\cdot,X^\ast,u^\ast)$, such that the inequality
\begin{equation}\label{eq:global exponential uniform stabilizability}
	\left|X(t,x^\ast,u^\ast)-X(t,x,k^\ast)\right|\leq Ce^{-\lambda t}|x^\ast-x|
\end{equation}
holds, for every $t\geq0$, and for every $x\in\mathbb{R}^n$ (\cite{Manchester2014a}). Note that this not is a particular case of \emph{incremental asymptotic stability}, the interested reader may address \cite{Forni2014,Forni2014a} for further information on this stability concept.

A stronger condition than the global exponential stabilizability of a particular solution is the requirement that every forward complete solution of the system is globally exponentially stabilizable. This concept is formalized in the following definition recalled from \cite{Manchester2014a}.

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} that globally exponentially uniformly stabilizes any forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}.
\end{definition}

@@

For each component $i\in\mathbb{N}_{[1,m]}$ of the feedback law $k^\ast=(k_1^\ast,\ldots,k_m^\ast)^\top$, denote the set of indexes
\begin{equation*}
	\mathscr{K}(i)=\left\{j\in\mathbb{N}_{[1,n]}:k_i^\ast\ \text{depends explicitely on}\ x_j \right\}.
\end{equation*}
The definition of the set $\mathscr{K}(\cdot)$ encompasses different structures. For instance when $m=n$, full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$. This is formalized by letting $\mathscr{K}(i)=\{i\}$. Moreover, at points where $k_i^\ast$ is differentiable, the explicit dependence on $x_i$ means that, for every index $j\in\mathbb{N}_{[1,n]}$ with $j\neq i$, $\partial k_i^\ast/\partial x_j\equiv0$.

@@

\begin{problem}\label{problem formulation}\hfill
	\begin{enumerate}
		\item Find a feedback law rendering system \eqref{eq:general system} universally stable;

		\item The function $k^\ast$ belongs to the set $\Xi$.
		\end{enumerate}
\end{problem}

The property described in item 2 of Problem \ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i.
	\end{array}\right.
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach cannot compute a unconstrained controller on a standard desktop machine, due to the number of variables. However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.

@@

A suitable notion to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by 
\begin{equation*}
	A_{jk}(x,u)=\dfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)	
\end{equation*}
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{align}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x\leq\ -2\lambda \delta_x^\top M\delta_x\label{eq:}
		\end{align}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition for exponential convergence of solutions. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

@@

\begin{theorem}\label{prop:CCM Existence}
	If there exists a control-contraction metric for system \eqref{eq:general system}, then a feedback law for system~\eqref{eq:general system} is obtained by integrating the feedback law for system~\eqref{eq:general system:differential}.
\end{theorem}

Theorem~\ref{prop:CCM Existence} provides the result needed to solve item 1 of Problem~\ref{problem formulation}.

As remarked in \cite{Manchester2014a}, the main advantage to look for control-contraction metric with over control-Lyapunov functions is that the former case can be formulate in terms of a convex optimization problem while the later is non-convex \cite{Rantzer:2001}. The steps to obtain a control to system \eqref{eq:general system} that solves item 1 of Problem~\ref{problem formulation} are shown below.

@@

From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} can not be distributely computed.

In this paper, these limitations are addressed by imposing a block-diagonal structure over $W$. Moreover, when $W$ is row-diagonal dominant, not only the solutions to the optimization problem \eqref{eq:geodesic formulation} can be computed in parallel but also the MI \eqref{eq:MI formulation}.

@@

Definition~\ref{def:SSCCM} implies that there exist integers $N>1$ and $n_i>0$ such that $n_1+\ldots+n_N=n$. Also, there exist smooth bounded functions $M_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ satisfying $M_i=M_i^\top\succ0$, for every index $i\in\mathbb{N}_{[1,N]}$, and the equation
	\begin{equation*}
		V(x,\delta_x)=\sum_{i=1}^N \delta_{x_i}^\top M_i(x_i)\delta_{x_i}=\sum_{i=1}^N V_i(x_i),
	\end{equation*}
for every $(x_i,\delta x_i)\in\mathbb{R}^{n_i}\times\mathbb{R}^{n_i}$. In other words, the metric $V$ for system \eqref{eq:general system} is decomposed into a sum of components $V_i$, where $i\in\mathbb{N}_{[1,N]}$, each one of these depend only on $i$-th component of the the system state $x$, i.e., $x_i\in\mathbb{R}^{n_i}$. The concept behind this definition is similar to the notion of sum-separable Lyapunov functions (see \cite{Dirr2015}).

@@

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

\begin{corollary}\label{cor:distributed computation}
	 If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI
	\begin{equation}\label{eq:MI formulation:i}
		T_{ii}\preceq 0
	\end{equation}
	for every index $i\in\mathbb{N}_{[1,N]}$, and the matrix $T$ is diagonally dominant, then pair of matrices $W$ and $Y$ is a solution to the MI \eqref{eq:MI formulation}.
\end{corollary}

@@

@@

Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
